
## Poetry Post Mapping Project

Poetry posts are scattered throughout Portland where neighbors offer us little gifts through poetry: a moment to pause, breathe, and receive inspiration, peace, delight, a new perspective, a sense of connection. We believe poetry posts strengthen our neighborhoods and build community.


## The Map

Below are the poetry posts we've identified so far. If you've found or built a post, [you can submit it here](https://forms.gle/egjDBjEq66V1x9hu9).

Last updated: `r Sys.Date()`

```{r, include = FALSE}
# ADD EMAIL TO FORM -- for infrequent updates
# OPT OUT?
# PHOTO
# Description: specific location (optional), anything else distinct 
# Unique feature (optional)

# LIST grouped by neighborhood
# URL: poetrypostspdx.org
# leaflet popup with description? photo option?

# filter by neighborhood

# put link to form above map
# maximize leaflet map button

# routing - pre computed by neighborhood?
# poetry post resources - page - builders
# for educators
#1 map
#2 form
#3 resources
#4 walks / for educators

# Number of people within 10 minute walk of poetry - 1

# street roots
```


```{r, include = FALSE}
library(tidyverse)
library(sf)
library(leaflet)
library(googlesheets4)
library(tidygeocoder)
library(leaflet.extras)
library(crosstalk)
library(DT)
locations <- read_sheet("https://docs.google.com/spreadsheets/d/1aeXAja0M0s7ZNB7eLedvgWtjP32i0MZkA6nOaGjzh6w/edit?usp=sharing")  %>%
  select(`Address of Poetry Post`, Verified)

locations_unverif <- read_sheet("https://docs.google.com/spreadsheets/d/1aeXAja0M0s7ZNB7eLedvgWtjP32i0MZkA6nOaGjzh6w/", range = "From Archive") %>% mutate("Address of Poetry Post" = paste(Address, city, "Oregon")) %>%
  select(`Address of Poetry Post`, Verified)

locations <- bind_rows(locations, locations_unverif) %>% 
  mutate(Verified = case_when(Verified == TRUE ~ "Yes",
                              TRUE ~ "No"
                              ))

#saveRDS(locations, "Data/loctemp.rds")



#geocoded_locs <- geocode(locations, address = `Address of Poetry Post`, method = 'arcgis')
#geocoded_locs <- filter(geocoded_locs, is.na(`Address of Poetry Post`)==FALSE)
#locs_sf <- st_as_sf(geocoded_locs, coords = c( "long", "lat"))
#st_crs(locs_sf) <- st_crs(4326)

neighborhoods <- st_read("Data/Neighborhood_Boundaries/") %>% st_transform(st_crs(4326))
labs <- st_centroid(neighborhoods)
locs_sf <- readRDS("locs_sf.rds") %>% unique()

locs_sf <- locs_sf %>% st_join(neighborhoods) %>% select(`Address of Poetry Post`, Neighborhood = "MAPLABEL", Verified)

locs_sf1 <- locs_sf %>% filter(Verified == "Yes")
locs_sf2 <- locs_sf %>% filter(Verified=="No")

sd <- SharedData$new(locs_sf1,  group = "Neighborhood")
sd2 <- locs_sf2


```



```{r, echo = FALSE, message=FALSE, warning=FALSE}
filter_select("Neighborhood", "Filter by Neighborhood", sd, group = ~Neighborhood)

your_map <- leaflet() %>%  
  addProviderTiles(providers$OpenStreetMap) %>%
  addMarkers(data= sd,
             icon = makeIcon("Fa-Team-Fontawesome-FontAwesome-Scroll.512.png",
                             iconWidth = 19, iconHeight = 19),
             label = ~`Address of Poetry Post`
             )%>%
    addMarkers(data= sd2,
             icon = makeIcon("question-circle-solid.png", iconWidth = 10, iconHeight = 10),
             label = ~`Address of Poetry Post`,
             group = "View Unverified Posts"
             )%>%
    addPolygons(data= neighborhoods, fillOpacity =0, opacity = 0.4,weight=1.5, group  = "View Neighborhood Boundaries"
                ) %>%
  addControlGPS(
      
    options = gpsOptions(
      position = "topleft",
      activate = TRUE, 
      autoCenter = TRUE,
      setView = TRUE,
      maxZoom=14
      ))%>%
    addFullscreenControl()%>%
  addLayersControl(overlayGroups = c("View Neighborhood Boundaries", "View Unverified Posts"), options = layersControlOptions(collapsed=FALSE)) %>%
  hideGroup("View Neighborhood Boundaries") %>%
  hideGroup("View Unverified Posts") %>%
  activateGPS()
your_map
```



