## Poetry Post Mapping Project

Poetry posts are scattered throughout Portland where neighbors offer us little gifts through poetry: a moment to pause, breathe, and receive inspiration, peace, delight, a new perspective, a sense of connection. We believe poetry posts strengthen our neighborhoods and build community.

## The Map

Below are the poetry posts we've identified so far. If you've found or built a post, [you can submit it here](https://forms.gle/egjDBjEq66V1x9hu9).

Last updated: `r Sys.Date()`

```{r, include = FALSE}
# ADD EMAIL TO FORM -- for infrequent updates
# OPT OUT?
# PHOTO
# Description: specific location (optional), anything else distinct 
# Unique feature (optional)

# LIST grouped by neighborhood
# URL: poetrypostspdx.org
# leaflet popup with description? photo option?

# filter by neighborhood

# put link to form above map
# maximize leaflet map button

# routing - pre computed by neighborhood?
# poetry post resources - page - builders
# for educators
#1 map
#2 form
#3 resources
#4 walks / for educators

# Number of people within 10 minute walk of poetry - 1

# street roots
```

```{r, include = FALSE}
library(tidyverse)
library(sf)
library(leaflet)
library(googlesheets4)
library(tidygeocoder)
library(leaflet.extras)
library(crosstalk)
library(DT)
locations <- read_sheet("https://docs.google.com/spreadsheets/d/1aeXAja0M0s7ZNB7eLedvgWtjP32i0MZkA6nOaGjzh6w/edit?usp=sharing")  %>%
  select(`Address of Poetry Post`, Verified)

locations_unverif <- read_sheet("https://docs.google.com/spreadsheets/d/1aeXAja0M0s7ZNB7eLedvgWtjP32i0MZkA6nOaGjzh6w/", range = "From Archive") %>% mutate("Address of Poetry Post" = paste(Address, city, "Oregon"))%>%
filter(remove_from_map == FALSE & Verified == FALSE)%>%
  select(`Address of Poetry Post`, Verified)

locations <- bind_rows(locations, locations_unverif) %>% 
  mutate(Verified = case_when(Verified == TRUE ~ "Yes",
                              TRUE ~ "No"
                              ))

#saveRDS(locations, "Data/loctemp.rds")



#geocoded_locs <- geocode(locations, address = `Address of Poetry Post`, method = 'arcgis')
#geocoded_locs <- filter(geocoded_locs, is.na(`Address of Poetry Post`)==FALSE)
#geocoded_locs <- dplyr::filter(geocoded_locs, is.na(long)==FALSE)


#locs_sf <- st_as_sf(geocoded_locs, coords = c( "long", "lat"))
#st_crs(locs_sf) <- st_crs(4326)

#saveRDS(locs_sf, "locs_sf.rds")

locs_sf <- readRDS("locs_sf.rds") %>% unique()

neighborhoods <- st_read("Data/Neighborhood_Boundaries/") %>% st_transform(st_crs(4326))
labs <- st_centroid(neighborhoods)

locs_sf <- locs_sf %>% 
  st_join(neighborhoods) %>% 
  select(`Address of Poetry Post`, Neighborhood = "MAPLABEL", Verified)

locs_sf1 <- locs_sf %>% filter(Verified == "Yes")
locs_sf2 <- locs_sf %>% filter(Verified=="No")

saveRDS(locs_sf1, "locs_sf_verif.rds")
sd <- SharedData$new(locs_sf1,  group = "Neighborhood")
sd2 <- locs_sf2
#sd2 <- SharedData$new(locs_sf2,  group = "Neighborhood")


```

```{r, echo = FALSE, message=FALSE, warning=FALSE}
filter_select("Neighborhood", "Filter by Neighborhood", sd, group = ~Neighborhood)

your_map <- leaflet() %>%  
      setView(lng = -122.6784, lat = 45.5152, zoom = 11
          ) %>%

  addProviderTiles(providers$OpenStreetMap) %>%
  addMarkers(data= sd,
             icon = makeIcon("Fa-Team-Fontawesome-FontAwesome-Scroll.512.png",
                             iconWidth = 19, iconHeight = 19),
             label = ~`Address of Poetry Post`
             )%>%
    addMarkers(data= sd2,
             icon = makeIcon("question-circle-solid.png", iconWidth = 10, iconHeight = 10),
             label = ~`Address of Poetry Post`,
             group = "View Unverified Posts"
             )%>%
    addPolygons(data= neighborhoods, fillOpacity =0, opacity = 0.4,weight=1.5, group  = "View Neighborhood Boundaries"
                ) %>%
  addControlGPS(
      
    options = gpsOptions(
      position = "topleft",
      activate = TRUE, 
      autoCenter = TRUE,
      setView = TRUE,
      maxZoom=14
      ))%>%
    addFullscreenControl()%>%
  addLayersControl(overlayGroups = c("View Neighborhood Boundaries", "View Unverified Posts"), options = layersControlOptions(collapsed=FALSE)) %>%
  hideGroup("View Neighborhood Boundaries") %>%
  hideGroup("View Unverified Posts") %>%
  activateGPS()
your_map
```

*We want to acknowledge the wonderful community members who have worked in the past to map poetry posts, some of whom are joining this effort. We have the good fortune of learning from and building on their efforts. Our gratitude to Matt B, Sue G, David C, John M, Richard L, Doug G, Tony P, Laurence C, Gus B, Christine T, Ruth L, and no doubt many others!*
