
## Poetry Post Mapping Project

Poetry posts are scattered throughout Portland where neighbors offer us little gifts through poetry: a moment to pause, breathe, and receive inspiration, peace, delight, a new perspective, a sense of connection. We believe poetry posts strengthen our neighborhoods and build community.


## The Map

Below are the poetry posts we've identified so far. If you've found or built a post, [you can submit it here](https://forms.gle/egjDBjEq66V1x9hu9).

Last updated: `r Sys.Date()`

```{r, include = FALSE}
# ADD EMAIL TO FORM -- for infrequent updates
# OPT OUT?
# PHOTO
# Description: specific location (optional), anything else distinct 
# Unique feature (optional)

# LIST grouped by neighborhood
# URL: poetrypostspdx.org
# leaflet popup with description? photo option?

# filter by neighborhood

# put link to form above map
# maximize leaflet map button

# routing - pre computed by neighborhood?
# poetry post resources - page - builders
# for educators
#1 map
#2 form
#3 resources
#4 walks / for educators

# Number of people within 10 minute walk of poetry - 1

# street roots
```


```{r, include = FALSE}
library(tidyverse)
library(sf)
library(leaflet)
library(googlesheets4)
library(tidygeocoder)
library(leaflet.extras)
library(crosstalk)
library(DT)
locations <- read_sheet("https://docs.google.com/spreadsheets/d/1aeXAja0M0s7ZNB7eLedvgWtjP32i0MZkA6nOaGjzh6w/edit?usp=sharing")

geocoded_locs <- geocode(locations, address = `Address of Poetry Post`, method = 'arcgis')
geocoded_locs <- filter(geocoded_locs, is.na(`Address of Poetry Post`)==FALSE)
locs_sf <- st_as_sf(geocoded_locs, coords = c( "long", "lat"))
st_crs(locs_sf) <- st_crs(4326)
neighborhoods <- st_read("Data/Neighborhood_Boundaries/") %>% st_transform(st_crs(4326))
labs <- st_centroid(neighborhoods)
locs_sf <- locs_sf %>% st_join(neighborhoods) %>% select(`Address of Poetry Post`, Neighborhood = "MAPLABEL")

saveRDS(locs_sf, "locs_sf.rds")
```


```{r, echo = FALSE, message=FALSE, warning=FALSE}
#filter_select("Neighborhood", "", sd, group= ~Neighborhood)
your_map <- leaflet(locs_sf) %>%  
  addProviderTiles(providers$OpenStreetMap) %>%
  addMarkers(data= locs_sf,
             icon = makeIcon("Fa-Team-Fontawesome-FontAwesome-Scroll.512.png", iconWidth = 19, iconHeight = 19),
             label = ~`Address of Poetry Post`,
             clusterOptions = markerClusterOptions()
             )%>%
    addPolygons(data= neighborhoods, fillOpacity =0, opacity = 0.4,weight=1.5, group  = "View Neighborhood Boundaries"
                ) %>%
  addControlGPS(
      
    options = gpsOptions(
      position = "topleft",
      activate = TRUE, 
      autoCenter = TRUE,
      setView = TRUE,
      maxZoom=14
      ))%>%
    addFullscreenControl()%>%
  addLayersControl(overlayGroups = "View Neighborhood Boundaries", options = layersControlOptions(collapsed=FALSE)) %>%
  hideGroup("View Neighborhood Boundaries") %>%
  activateGPS()
your_map
```



