
## Poetry Post Mapping Project

Poetry posts are scattered throughout Portland where neighbors offer us little gifts through poetry: a moment to pause, breathe, and receive inspiration, peace, delight, a new perspective, a sense of connection. We believe poetry posts strengthen our neighborhoods and build community.


## The Map

Below are the poetry posts we've identified so far.

Last updated: November 2023

```{r, include = FALSE}
library(tidyverse)
library(sf)
library(leaflet)
library(googlesheets4)
library(tidygeocoder)
locations <- read_sheet("https://docs.google.com/spreadsheets/d/1aeXAja0M0s7ZNB7eLedvgWtjP32i0MZkA6nOaGjzh6w/edit?usp=sharing")

geocoded_locs <- geocode(locations, address = `Address of Poetry Post`, method = 'arcgis')

locs_sf <- st_as_sf(geocoded_locs, coords = c( "long", "lat"))
st_crs(locs_sf) <- st_crs(4326)
```

```{r, echo = FALSE, message=FALSE}
leaflet(locs_sf) %>%
  addProviderTiles(provider = providers$CartoDB.Positron) %>%
  addMarkers(icon = makeIcon("Fa-Team-Fontawesome-FontAwesome-Scroll.512.png", iconWidth = 30, iconHeight = 30),
             label = ~`Address of Poetry Post`)
```

